Are environmental and geographic variables effective surrogates for genetic variation in conservation planning?

### 2016-03-23 article/figures.Rmd
+ new parameters + fixes with figures

```{r, echo=FALSE, fig.width=6, fig.height=4.5, fig.cap='The relationship between surrogates and genetic variation secured in prioritizations. Panel (a) shows the relationship between environmental surrogate targets used to generate a prioritization and the proportion of adaptive genetic variation it secures. Similarly, panel (b) shows that for geographic surrogate targets and neutral genetic variation. Box-plots show inter-specific variation in the proportion of genetic variation secured using different surrogate-based targets. Letters indicate significant differences ($P < 0.05$).'}
# prepare data
env.correlation.DF$Surrogate.target <- factor(env.correlation.DF$Surrogate.target)
env.correlation.DF2 <- env.correlation.DF %>%
	group_by(Surrogate.target, Method, Type) %>% 
	summarize(genetic.held=max(genetic.held, na.rm=TRUE)+0.1) %>%
	ungroup() %>% mutate(Combination=as.character(paste0(Surrogate.target,'.',Method,'.',Type))) %>% 
	left_join(
		data.frame(
			letter=unname(toupper(cld(posthoc.correlation.GLHT)$mcletters$Letters)),
			Combination=as.character(names(toupper(cld(posthoc.correlation.GLHT)$mcletters$Letters))),
			stringsAsFactors=FALSE
		),
		by='Combination'
	) %>% data.frame()
geo.correlation.DF$Surrogate.target <- factor(geo.correlation.DF$Surrogate.target)
geo.correlation.DF2 <- geo.correlation.DF %>%
	group_by(Surrogate.target, Method, Type) %>% 
	summarize(genetic.held=max(genetic.held, na.rm=TRUE)+0.1) %>%
	ungroup() %>% mutate(Combination=as.character(paste0(Surrogate.target,'.',Method,'.',Type))) %>% 
	left_join(
		data.frame(
			letter=unname(toupper(cld(posthoc.correlation.GLHT)$mcletters$Letters)),
			Combination=as.character(names(toupper(cld(posthoc.correlation.GLHT)$mcletters$Letters))),
			stringsAsFactors=FALSE
		),
		by='Combination'
	) %>% data.frame()

# make figure
p1 <- ggplot(aes(x=Surrogate.target,y=genetic.held, color=Method),
		data=env.correlation.DF) +
	geom_boxplot(position=position_dodge(0.9)) +
	xlab('Environmental surrogate target (%)') + 
	ylab('Adaptive genetic\nvariation secured (%)') +
	geom_text(aes(x=0.75, y=1, label='(a)'), color='black', size=5) +
	theme_classic() +
	theme(legend.position=c(0.225,0.8)) +
	scale_color_manual(name='Prioritization', values=c('Optimal'='black', 'Random'='grey50')) +
	geom_text(aes(x=Surrogate.target, y=genetic.held, color=Method, label=letter),
		data=env.correlation.DF2, position=position_dodge(0.9))

p2 <- ggplot(aes(x=Surrogate.target,y=genetic.held, color=Method),
			data=geo.correlation.DF) +
	geom_boxplot(position=position_dodge(0.9)) +
	xlab('Geographic surrogate target (%)') + 
	ylab('Neutral genetic\nvariation secured (%)') +
	geom_text(aes(x=0.75, y=1, label='(b)'), color='black', size=5) +
	theme_classic() +
	theme(legend.position='none') +
	scale_color_manual(name='Prioritization', values=c('Optimal'='black', 'Random'='grey50')) +
	geom_text(aes(x=Surrogate.target, y=genetic.held, color=Method, label=letter),
		data=geo.correlation.DF2, position=position_dodge(0.9))

@@

```{r, echo=FALSE, warning=FALSE, message=FALSE, fig.width=5, fig.height=5, fig.cap='Planning unit selection frequencies. The top row of panels (a, b, c) show single-species prioritizations generated assuming equal costs. The middle row of panels (d, e, f) show multi-species prioritizations generated assuming equal costs. The bottom row of panels (g, h, i) show multi-species generated using opportunity costs. The left column of panels (a, d, g) show prioritizations generated using only amount-based targets. The middle column of panels (b, e, h) show prioritizations generated using amount- and surrogate-based targets. The right column of panels (c, f, i) show prioritizations generated using amount- and genetic-based targets.'}
# download basemap
data(countriesHigh)
countries.FPLY <- countriesHigh[
	countriesHigh$ADMIN %in% c(
		'Italy', 'Switzerland', 'France', 'Austria',
		'Germany', 'Slovenia', 'Croatia', 'Hungary',
		'Monaco', 'Germany', 'Slovakia', 'Czech Republic'
	)
,] %>% spFortify
# prepare data for plotting
grid.FPLY <- grid.PLY
for (i in seq_along(single.spp.prioritisations))
	grid.FPLY@data[[paste0('Single-species (equal costs).', c('Amount', 'Surrogate', 'Genetic')[i])]] <- rowMeans(sapply(single.spp.prioritisations[[i]], function(x){colMeans(x@results@selections)}))
for (i in seq_along(multi.spp.prioritisations))
	grid.FPLY@data[[paste0('Multi-species (equal costs).', c('Amount', 'Surrogate', 'Genetic')[i])]] <- colMeans(multi.spp.prioritisations[[i]]@results@selections)
for (i in seq_along(multi.spp.prioritisations.with.cost))
	grid.FPLY@data[[paste0('Multi-species (opportunity costs).', c('Amount', 'Surrogate', 'Genetic')[i])]] <- colMeans(multi.spp.prioritisations.with.cost[[i]]@results@selections)
grid.FPLY <- spFortify(grid.FPLY)
grid.FPLY <- grid.FPLY %>% gather(
		Combination,
		`Selection.Frequency`,
		`Single-species (equal costs).Amount`:`Multi-species (opportunity costs).Genetic`
	) %>% mutate(
		Context=sapply(strsplit(as.character(Combination), '.', fixed=TRUE), `[[`, 1),
		Prioritization=sapply(strsplit(as.character(Combination), '.', fixed=TRUE), `[[`, 2)
	) %>% mutate(
		Prioritization=factor(Prioritization, levels=c('Amount', 'Surrogate', 'Genetic')),
		Context=factor(
			gsub(' (', '\n(', Context, fixed=TRUE),
			levels=c("Single-species\n(equal costs)", "Multi-species\n(equal costs)", 
			"Multi-species\n(opportunity costs)"))
	)
panel.DF <- grid.FPLY %>% select(Context, Prioritization, long, lat) %>% 
	mutate(
		lat=min(lat)+(diff(range(lat))*0.98),
		long=min(long)+(diff(range(long))*0.02)
	) %>%
	group_by(Context,Prioritization) %>% filter(c(TRUE, rep(FALSE, length(Context)-1))) %>%
	mutate(
		panel.letter=paste0('(',letters[(as.integer(Context)-1)*3 + as.integer(Prioritization)],')'),
		panel.letter=c(as.character(panel.letter[1]), rep(NA_character_, length(Context)-1))
	)
# make maps
ggplot() +
	geom_polygon(data=countries.FPLY, aes(x=long, y=lat, group=group),
		fill='grey85', color='grey70') +
	geom_polygon(data=grid.FPLY, aes_string(x='long', y='lat', 
		group='group', fill='Selection.Frequency'),
		alpha=0.8, color='grey10') +
	geom_text(aes_string(x='long',y='lat', label='panel.letter'), data=panel.DF) +
	theme_classic() +
	theme(axis.ticks=element_blank(), axis.text=element_blank(),
		plot.margin=unit(c(0,0,0,0),'cm'), axis.line=element_blank(),
		strip.background = element_rect(fill='grey20'),
		strip.text = element_text(color='white'),
		legend.position='bottom', legend.key.width=unit(1.8, 'cm'),
		legend.title=element_text(vjust=-5),
		legend.margin=unit(c(0.1), 'cm'),
		axis.title=element_blank()) +
	coord_cartesian(
		xlim=buffered.range(grid.FPLY$long, 0),
		ylim=buffered.range(grid.FPLY$lat, 0)
	) +
	facet_grid(Context ~ Prioritization) +
	scale_fill_gradientn(name='Selection Frequency (%)',
		colors=brewer.pal(9, 'PuBu'),
		guide=guide_colorbar(title.position='bottom', title.hjust=0.5,
			ticks=element_line(color='black'), border=element_line(color='black'))
	)
```

@@

# make plot
suppressWarnings({
	ggplot(aes(x=Prioritisation,y=value),
		data=results.SDF) +
		geom_boxplot(position=position_dodge(0.9)) +
		geom_text(aes(x=Prioritisation, y=letter.height, label=letter),
			data=results.PDF, position=position_dodge(0.9)) +
		geom_text(aes(x=0.7, y=1, label=panel.letter),
			data=results.PDF) +
		scale_fill_manual(name='Prioritisation',
			values=c('grey80','grey50','grey20')) +
		ylab('Genetic variation secured (%)') +
		xlab('') +
		scale_y_continuous(breaks=c(0,0.25,0.5,0.75,1), limits=c(NA, 1.2)) +
		theme_classic() +
		theme(strip.background = element_rect(fill='grey20'),
			strip.text = element_text(color='white'),
			panel.border = element_rect(color='black', fill=NA),
			axis.text.x=element_text(angle=45, hjust=1, vjust=1)) +
		facet_grid(Context ~ Metric)
})
```

>>>>

```{r, echo=FALSE, message=FALSE, fig.width=6, fig.height=4.5, fig.cap='The relationship between surrogates and genetic variation secured in prioritizations. Panel (a) shows the relationship between environmental surrogate targets used to generate a prioritization and the proportion of adaptive genetic variation it secures. Similarly, panel (b) shows that for geographic surrogate targets and neutral genetic variation. Box-plots show inter-specific variation in the proportion of genetic variation secured using different surrogate-based targets. Letters indicate significant differences ($P < 0.05$).'}
# prepare data
env.correlation.DF$Surrogate.target <- factor(env.correlation.DF$Surrogate.target)
env.correlation.DF2 <- env.correlation.DF %>%
	group_by(Surrogate.target, Method, Type) %>% 
	summarize(genetic.held=max(genetic.held, na.rm=TRUE)+0.1) %>%
	ungroup() %>% mutate(Combination=as.character(paste0(Surrogate.target,'.',Method,'.',Type))) %>% 
	left_join(
		data.frame(
			letter=unname(toupper(cld(posthoc.correlation.GLHT)$mcletters$Letters)),
			Combination=as.character(names(toupper(cld(posthoc.correlation.GLHT)$mcletters$Letters))),
			stringsAsFactors=FALSE
		),
		by='Combination'
	) %>% data.frame()

geo.correlation.DF$Surrogate.target <- factor(geo.correlation.DF$Surrogate.target)
geo.correlation.DF2 <- geo.correlation.DF %>%
	group_by(Surrogate.target, Method, Type) %>% 
	summarize(genetic.held=max(genetic.held, na.rm=TRUE)+0.1) %>%
	ungroup() %>% mutate(Combination=as.character(paste0(Surrogate.target,'.',Method,'.',Type))) %>% 
	left_join(
		data.frame(
			letter=unname(toupper(cld(posthoc.correlation.GLHT)$mcletters$Letters)),
			Combination=as.character(names(toupper(cld(posthoc.correlation.GLHT)$mcletters$Letters))),
			stringsAsFactors=FALSE
		),
		by='Combination'
	) %>% data.frame()

# make figure
p1 <- ggplot(aes(x=Surrogate.target,y=genetic.held, color=Method),
		data=env.correlation.DF) +
	geom_boxplot(position=position_dodge(0.9)) +
	xlab('Environmental surrogate target (%)') + 
	ylab('Adaptive genetic\nvariation secured (%)') +
	geom_text(aes(x=0.55, y=1.125, label='(a)'), color='black', size=5) +
	theme_classic() +
	theme(legend.position=c(0.9,0.4)) +
	scale_color_manual(name='Prioritization', values=c('Optimal'='black', 'Random'='grey50')) +
	geom_text(aes(x=Surrogate.target, y=genetic.held, color=Method, label=letter),
		data=env.correlation.DF2, position=position_dodge(0.9))

p2 <- ggplot(aes(x=Surrogate.target,y=genetic.held, color=Method),
			data=geo.correlation.DF) +
	geom_boxplot(position=position_dodge(0.9)) +
	xlab('Geographic surrogate target (%)') + 
	ylab('Neutral genetic\nvariation secured (%)') +
	geom_text(aes(x=0.55, y=1.125, label='(b)'), color='black', size=5) +
	theme_classic() +
	theme(legend.position='none') +
	scale_color_manual(name='Prioritization', values=c('Optimal'='black', 'Random'='grey50')) +
	geom_text(aes(x=Surrogate.target, y=genetic.held, color=Method, label=letter),
		data=geo.correlation.DF2, position=position_dodge(0.9))

@@

```{r, echo=FALSE, warning=FALSE, message=FALSE, fig.width=5, fig.height=5, fig.cap='Planning unit selection frequencies. The top row of panels (a, b, c) show single-species prioritizations generated assuming equal costs. The middle row of panels (d, e, f) show multi-species prioritizations generated assuming equal costs. The bottom row of panels (g, h, i) show multi-species generated using opportunity costs. The left column of panels (a, d, g) show prioritizations generated using only amount-based targets. The middle column of panels (b, e, h) show prioritizations generated using amount- and surrogate-based targets. The right column of panels (c, f, i) show prioritizations generated using amount- and genetic-based targets.'}
# download basemap
data(countriesHigh)
countries.FPLY <- countriesHigh[
	countriesHigh$ADMIN %in% c(
		'Italy', 'Switzerland', 'France', 'Austria',
		'Germany', 'Slovenia', 'Croatia', 'Hungary',
		'Monaco', 'Germany', 'Slovakia', 'Czech Republic'
	)
,] %>% spFortify
# prepare data for plotting
grid.FPLY <- grid.PLY
for (i in seq_along(single.spp.prioritisations[[1]]))
	grid.FPLY@data[[paste0('Single-species (equal costs).', c('Amount', 'Surrogate', 'Genetic')[i])]] <- rowMeans(sapply(single.spp.prioritisations, function(x){colMeans(x[[i]]@results@selections)}))
for (i in seq_along(multi.spp.prioritisations))
	grid.FPLY@data[[paste0('Multi-species (equal costs).', c('Amount', 'Surrogate', 'Genetic')[i])]] <- colMeans(multi.spp.prioritisations[[i]]@results@selections)
for (i in seq_along(multi.spp.prioritisations.with.cost))
	grid.FPLY@data[[paste0('Multi-species (opportunity costs).', c('Amount', 'Surrogate', 'Genetic')[i])]] <- colMeans(multi.spp.prioritisations.with.cost[[i]]@results@selections)
grid.FPLY <- spFortify(grid.FPLY)
grid.FPLY <- grid.FPLY %>% gather(
		Combination,
		`Selection.Frequency`,
		`Single-species (equal costs).Amount`:`Multi-species (opportunity costs).Genetic`
	) %>% mutate(
		Context=sapply(strsplit(as.character(Combination), '.', fixed=TRUE), `[[`, 1),
		Prioritization=sapply(strsplit(as.character(Combination), '.', fixed=TRUE), `[[`, 2)
	) %>% mutate(
		Prioritization=factor(Prioritization, levels=c('Amount', 'Surrogate', 'Genetic')),
		Context=factor(
			gsub(' (', '\n(', Context, fixed=TRUE),
			levels=c("Single-species\n(equal costs)", "Multi-species\n(equal costs)", 
			"Multi-species\n(opportunity costs)"))
	)
panel.DF <- grid.FPLY %>% select(Context, Prioritization, long, lat) %>% 
	mutate(
		lat=min(lat)+(diff(range(lat))*0.98),
		long=min(long)+(diff(range(long))*0.02)
	) %>%
	group_by(Context,Prioritization) %>% filter(c(TRUE, rep(FALSE, length(Context)-1))) %>%
	mutate(
		panel.letter=paste0('(',letters[(as.integer(Context)-1)*3 + as.integer(Prioritization)],')'),
		panel.letter=c(as.character(panel.letter[1]), rep(NA_character_, length(Context)-1))
	)
# make maps
ggplot() +
	geom_polygon(data=countries.FPLY, aes(x=long, y=lat, group=group),
		fill='grey85', color='grey70') +
	geom_polygon(data=grid.FPLY, aes_string(x='long', y='lat', 
		group='group', fill='Selection.Frequency'),
		alpha=0.8, color='grey10') +
	geom_text(aes_string(x='long',y='lat', label='panel.letter'), data=panel.DF) +
	theme_classic() +
	theme(axis.ticks=element_blank(), axis.text=element_blank(),
		plot.margin=unit(c(0,0,0,0),'cm'), axis.line=element_blank(),
		strip.background = element_rect(fill='grey20'),
		strip.text = element_text(color='white'),
		legend.position='bottom', legend.key.width=unit(1.8, 'cm'),
		legend.title=element_text(vjust=-5),
		legend.margin=unit(c(0.1), 'cm'),
		axis.title=element_blank()) +
	coord_cartesian(
		xlim=buffered.range(grid.FPLY$long, 0),
		ylim=buffered.range(grid.FPLY$lat, 0)
	) +
	facet_grid(Context ~ Prioritization) +
	scale_fill_gradientn(name='Selection Frequency (%)',
		colors=brewer.pal(9, 'PuBu'),
		guide=guide_colorbar(title.position='bottom', title.hjust=0.5,
			ticks=element_line(color='black'), border=element_line(color='black'))
	)
```

@@

# make plot
suppressWarnings({
	ggplot(aes(x=Prioritisation,y=value),
		data=results.SDF) +
		geom_boxplot(position=position_dodge(0.9)) +
		geom_text(aes(x=Prioritisation, y=letter.height, label=letter),
			data=results.PDF, position=position_dodge(0.9)) +
		geom_text(aes(x=0.7, y=1.05, label=panel.letter),
			data=results.PDF) +
		scale_fill_manual(name='Prioritisation',
			values=c('grey80','grey50','grey20')) +
		ylab('Genetic variation secured (%)') +
		xlab('') +
		scale_y_continuous(breaks=c(0,0.25,0.5,0.75,1), limits=c(NA, 1.2)) +
		theme_classic() +
		theme(strip.background = element_rect(fill='grey20'),
			strip.text = element_text(color='white'),
			panel.border = element_rect(color='black', fill=NA),
			axis.text.x=element_text(angle=45, hjust=1, vjust=1)) +
		facet_grid(Context ~ Metric)
})
```
